Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-19 paper.qmd
Try to add more plots

```{r}
#| label: diff-bins-scurve
## To initialize benchmark values to remove low density hexagons
benchmark_rm_hex_vec <- seq(0, 0.8, by=0.1)
bin1_vec_scurve <- c(7, 11, 17)
error_rm_scurve <- data.frame(matrix(nrow = 0, ncol = 0))

@@

@@

@@

<!--distribution of distance along with the default benchmark-->
```{r}
#| label: triangulate-scurve2
## Triangulate bin centroids
tr1_object_scurve <- tri_bin_centroids(
  df_bin_centroids_scurve_keep, x = "c_x", y = "c_y")
tr_from_to_df_scurve <- gen_edges(
  tri_object = tr1_object_scurve)

@@

# Define bin width and starting point
bin_width <- hb_obj_scurve$centroids$c_x[2]-hb_obj_scurve2$centroids$c_x[1]
start_point <- bin_width/2

>>>>

```{r}
#| label: diff-bins-scurve-buff
## To initialize benchmark values to remove low density hexagons
benchmark_rm_hex_vec <- seq(0, 0.7, by=0.1)
bin1_vec_scurve <- c(7, 11, 17)
error_rm_scurve <- data.frame(matrix(nrow = 0, ncol = 0))

@@

    a1 <- calc_bins_y(bin1 = xbins, r2 = r2, q = 0.07)$a1

@@

    tr1_object_scurve <- tri_bin_centroids(
      df_bin_centroids_scurve_high_dens, 
      x = "c_x", 
      y = "c_y")

    tr_from_to_df_scurve <- gen_edges(
      tri_object = tr1_object_scurve)

@@

<!--distribution of distance along with the default benchmark-->

```{r}
#| label: diff-bins-scurve-buff3
#| eval: false
## To initialize benchmark values to remove low density hexagons
benchmark_rm_hex_vec <- seq(0, 0.7, by=0.1)
bin1_vec_scurve <- c(7, 11, 17)
distance_all_scurve <- data.frame(matrix(nrow = 0, ncol = 0))
#buffer_vec <- 0.07

  #for (benchmark_rm_lwd in benchmark_rm_hex_vec) {

    a1 <- calc_bins_y(bin1 = xbins, r2 = r2, q = buff)$a1

    tr1_object_scurve <- tri_bin_centroids(
      df_bin_centroids_scurve_high_dens, 
      x = "c_x", 
      y = "c_y")

    tr_from_to_df_scurve <- gen_edges(
      tri_object = tr1_object_scurve)

    start_point <- a1/2

    # Create bins and calculate the mean value for each bin range
    bins <- seq(start_point, max(distance_scurve$distance) + a1, 
                by = a1)
    bin_labels <- bins[-length(bins)] + a1 / 2  # mean of each bin range

    ## Compute error
    distance_scurve <- distance_scurve |>
      mutate(q = buff,
             bin1 = xbins,
             a1 = a1)

    distance_all_scurve <- bind_rows(distance_all_scurve, distance_scurve)

# dist_summary_scurve <- distance_all_scurve |>
#     count(bin1, q, bin)

distance_hist <- distance_all_scurve |>
  filter(bin1 == 11) |>
  filter(q == 0.07) |>
  ggplot(aes(x = distance)) +
    geom_histogram(
      aes(y = after_stat(count) / sum(after_stat(count)), 
      group = as.factor(q),
      fill = as.factor(q)),
      binwidth = a1,
      position = "dodge") +
  scale_x_continuous(breaks = bin_labels, labels = round(bin_labels, 3)) +
  scale_color_brewer(type = "qual") +
  #facet_wrap(vars(as.factor(bin1)), scale = "free") +
  ylab("standardized number of edges") +
  xlab(expression(d^{(2)})) +
  ggtitle("(d)") +
  theme(aspect.ratio = 0.75,
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12, angle = 90),
        axis.text.x = element_text(size = 12, angle = 90),
        axis.text.y = element_text(size = 12),
        axis.ticks.x = element_line(), 
        plot.title = element_text(size = 12))

```{r}
#| label: triangulate-scurve2

## Triangulate bin centroids
tr1_object_scurve <- tri_bin_centroids(
  df_bin_centroids_scurve_keep, x = "c_x", y = "c_y")
tr_from_to_df_scurve <- gen_edges(
  tri_object = tr1_object_scurve)

@@

# Define bin width and starting point
bin_width <- hb_obj_scurve2$centroids$c_x[2]-hb_obj_scurve2$centroids$c_x[1]
start_point <- bin_width/2
